Fluoroproj: Title to be decided later

### 2023-03-31 manuscript/manuscript_sds.qmd
updated manuscript

The goal of this paper is to compare accuracy and precision of a variety of fluorometers with respect to chlorophyll and phycocyanin across a variety of waterbodies as well as with lab grown cultures of green algae and cyanobacteria.

>>>>

The goal of this paper is to compare different handheld or in situ fluorometers with respect to a common benchmark (extracted chlorophyll and phycocyanin) in order to assess the feasibility of combining data from these various sources.

Old Goal: The goal of this paper is to compare accuracy and precision of a variety of fluorometers with respect to chlorophyll and phycocyanin across a variety of waterbodies as well as with lab grown cultures of green algae and cyanobacteria.
